---
title: "Week 2 Peer Review"
output: html_document
author: "Xuan Tung Hoang"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data.

## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.

```{r exercise1,echo=FALSE}

ideo5_1 <- recode(
  cces$ideo5,
  "1" = "Very Liberal",
  "2" = "Liberal",
  "3"= "Moderate",
  "4" = "Conservative",
  "5" = "Very Conservative"
)

cces_1 <- add_column(cces, ideo5_1)

p1 <- ggplot(cces_1, aes(x = ideo5_1, fill = ideo5_1)) +
  geom_bar() +
  guides(fill = "none") +
  labs(title = "Respondent Ideology", x = "Ideology", y = "Count")

p1

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}

pew_religimp_1 <- recode(
  cces$pew_religimp,
  "1" = "Very important",
	"2" = "Somewhat important",
	"3" = "Not too important",
	"4" = "Not at all important"
)

cces_2 <- add_column(cces_1, pew_religimp_1)

p2 <- ggplot(cces_2, aes(x = pew_religimp_1, fill = ideo5_1)) +
  geom_bar() +
  labs(title = "Importance of Religion by Ideology", x = "Importance of Religion", y = "Count", fill = "Ideology")

p2

```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your values will be slightly different):


```{r exercise3,echo=FALSE}

semester <- c(seq(from = 1,to = 6, by= 1))
student <- c("Amanda", "Betty", "Carol")

my_dat <- expand.grid(semester, student)

grade <- runif(18, 80, 100)

my_dat <- add_column(my_dat, grade)
  
my_dat <- rename(
    my_dat,
    "Semester" = Var1,
    "Student" = Var2,
    "Grade" = grade
  ) 

my_dat <- as_tibble(my_dat)

p3 <- ggplot(my_dat, aes(x = Semester, y = Grade, color = Student)) +
  geom_line() +
  guides(color = "none") +
  labs(title = "Student Grades by Semester", x = "Semester", y = "Grade") +
  facet_wrap(~Student)

p3

```
